\chapter{Conclusion}
\thispagestyle{empty}

Text classification is relatively new problem in Bangla Language Processing (BLP). Main challenge for a classification system is to develop a good quality dataset which can be used to teach our system or give our system a knowledge base from which it can fulfill our key objectives. In this project of ours, we also face the same problem lack of available dataset. We have built a dataset of suspicious text to implement this project.\par \vspace{0.5cm}
Our main contribution is that we develop a system which can classify a Bengali text into suspicious and non suspicious category. Another contribution is we develop a dataset of suspicious text which can be used for further research. We use different machine learning algorithm, evaluate them and shows a comparison of accuracy between this algorithms. This results will be helpful when someone will develop a system like this one. Our system obtains maximum accuracy of 92\% for Logistic Regression. To the best of our knowledge, it is the very first system which can detect a suspicious Bangla text.
\par \vspace{0.5cm}
Our system has some limitation like using limited number of document, training time. For this reasons we could not able to use our entire collection of data in training.
\section{Future Improvement}
The main purpose of our project was to develop a system for detecting suspicious Bangla texts using supervised machine learning. Here we give a Bengali text document as input and it will give us a feedback whether the text is suspicious or not. Our system can be improved in different areas,\\
\begin{itemize}
    \item We will use deep learning approach to find semantic relation between words of a text which will help us to predict more accurately.
    \item Include more data at corpus.
    \item Categorize the texts from most suspicious to less suspicious so that anyone can use it more easily.
    \item Our plan is to develop a web based system which can filter different online posts, writings and alert about suspicious activities.
\end{itemize}